Assignment 1
========================================================
Reading the 


```{r}
activity <- read.csv("activity.csv")

##converting variable interval to factor variable
activity$interval <- factor(activity$interval)
```

Plotting histogram of the total number of steps taken each day

```{r fig.width=7, fig.height=6}
histogram(activity$steps, xlab="Steps per Day", ylab="% Number of Days")
```

##Calculate and report the mean and median total number of steps taken per day
```{r}
steps_mm <- c("Date", "Mean Steps", "Median Steps")
for (i in levels(activity$date)){
  sub_act <- subset(activity, activity$date==i)
  steps_mm <- c(steps_mm, i, mean(sub_act$steps, na.rm=T), median(sub_act$steps, na.rm=T))
}
print (steps_mm)
```

Plotting average stetps per interval across dates
```{r}
steps <- c()
interval <- c()
max_steps <- c()
for (i in levels(activity$interval)){
  sub_act <- subset(activity, activity$interval==i)
  ##interval <- c(interval, i)
  if (mean(sub_act$steps, na.rm=T) > max(steps)){ max_steps <- c(i)}
  steps <- c(steps, mean(sub_act$steps, na.rm=T))
}

plot (steps, type="l", xlab="Time Interval", ylab="Average Steps", main="Average Steps across interval")
max_steps
```

Counting number of rows containing NA
```{r}
narow <- 0
for (i in 1:nrow(activity)){
  nacount <-0
  for (j in 1:ncol(activity)){
    if (is.na(activity[[i,j]])){
      nacount <- nacount +1
    }
  }
  if (nacount ==0){narow <- narow +1}
}
narow
```

Creating new data set containing replaced NA values with day's mean or 0 if nan

```{r}
new_Act <- activity
newMean <- 0
for (i in 1:nrow(new_Act)){
  if (is.na(new_Act$steps[i])){
    sub_act <- subset(new_Act, new_Act$date==new_Act$date[i])
    newMean <- mean(sub_act$steps, na.rm=T)
    if (is.nan(newMean)){
      new_Act$steps[i] <- 0
    }
    else {new_Act$steps[i]<- newMean}
  }
}
```
Histogram of the total number of steps taken each day on NA replacced dataset
```{r}
histogram(new_Act$steps, xlab="Steps per Day", ylab="% Number of Days")
```
Calculate and report the mean and median total number of steps taken per day

```{r}steps_mm_new <- c("Date", "Mean Steps", "Median Steps")
for (i in levels(new_Act$date)){
  sub_act <- subset(new_Act, new_Act$date==i)
  steps_mm_new <- c(steps_mm_new, i, mean(sub_act$steps, na.rm=T), median(sub_act$steps, na.rm=T))
}
print (steps_mm_new)
```

Are there differences in activity patterns between weekdays and weekends?
```{r}
new_Act$date<- as.Date(new_Act$date)
new_Act$day <- weekdays(new_Act$date)
new_Act$day <- factor(new_Act$day)
new_Act$wkday <- new_Act$day
if (new_Act$wkday == "Sunday"){new_Act$wkday <- 0}
if (new_Act$wkday == "Saturday"){ new_Act <- 0}
if (new_Act$wkday == "Monday"){new_Act$wkday <- 1}
if (new_Act$wkday == "Tuesday"){new_Act$wkday <- 1}
if (new_Act$wkday == "Wednesday"){new_Act$wkday <- 1}
if (new_Act$wkday == "Thursday"){new_Act$wkday <- 1}
if (new_Act$wkday == "Friday"){new_Act$wkday <- 1}

new_Act$wkday <- factor(new_Act$wkday, levels=c("Weekdays", "Weekend"))

xyplot(steps~interval | new_Act$wkday, type = "l", layout=c(1,2))
```
